Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-11-25 analysis/paper/paper.Rmd
notes on background

@@

ggplot(mydata_ages, 
       aes(x = age_ka,
           y = `altitude(m)_of_main_layer`,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16) 
```

>>>>

<!-- one equal-sized paragraph for each of our three questions, with lots of recent, specific citations for each Q -->

@@

ggplot(mydata_ages, 
       aes(x = age_ka,
           y = `altitude(m)_of_main_layer`,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)

ggsave(here("analysis/figures/site-elevation-by-age.png"))
```
